Model-based pretreatment for regression with correlated variables.

### 2014-04-01 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@492 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\subsection{A by-product model: marginal regression with decorrelated covariates}
Let $\boldsymbol{Y} \in \mathcal{R}^n$ be a response variable we want to explain with $X$:
	\begin{equation}
			Y_{|S,X}=X\beta+\varepsilon_Y =X_1\beta_1+X_2\beta_2+\varepsilon_Y \textrm{ with } \varepsilon_Y \sim \mathcal{N}(0,\sigma^2_YI_n);	\label{MainR}
		\end{equation}
		where $\beta=(\beta_1,\beta_2) \in  \mathcal{R}^p$ is the vector of the regression coefficients and $I_n$ the identity matrix. 
We note that (\ref{MainR}) and (\ref{SR}) also give by simple integration on $X_2$ a regression model on $Y$ {\it depending only on uncorrelated covariates $X_1$}:
\begin{eqnarray}
	Y_{|X_1}&=&X_1 (\beta_{1}+ \sum_{j \in I_2}\beta_{j}\delta_j)+  \sum_{j \in I_2}\beta_{j}\varepsilon_{j}+\varepsilon_Y \label{Trueexpl} \\
		&=&X_1 \alpha_1 + X_2\alpha_2 + \varepsilon_{\alpha} \textrm{ where } \alpha_2  = 0.
\end{eqnarray}
We note that it simply is a linear regression on some of the original covariates so we only made a pretreatment on the dataset by setting some coefficients to $0$ because of correlations. These $0$ won't be interpreted as independence with the response variable but as redundant information due to correlations between the covariates. It is a variable pre-selection independent of the response $Y$. As a pretreatment, it allows usage of any method in a second time to estimate $\alpha$like LASSO or even stepwise \cite{seber2012linear}.

\subsection{Strategy of use: pretreatment before classical selection methods}\label{interpretation}
The explicit structure is parsimonious and simply consists in linear regressions and thus is easily understood by non statistician, allowing them to have a better knowledge of the phenomenon inside the dataset. Expert knowledge can even be added to the structure.

@@

\bibliography{biblio}{}
\bibliographystyle{plain}
\section{Appendices}
	\subsection{Identifiability of the structure}
	The model presented above relies on a discrete structure $S$ between the covariates. But to find it we need identifiability property to insure the MCMC will asymptotically find the true model. Identifiability of the discrete structure is asked in following terms: Is it possible to find another structure $\tilde{S}$ of linear regression between the covariates leading to the same joint distribution and marginal distributions? The answer is no. Thus $S$ is identifiable.

>>>>

\subsection{A by-product model: marginal regression with decorrelated covariates}
Let $\boldsymbol{Y} \in \mathcal{R}^n$ be a response variable we want to explain with $\boldsymbol{X}$:
	\begin{equation}
			\boldsymbol{Y}_{|\boldsymbol{X_1},\boldsymbol{X_2},S}=\boldsymbol{X_1\beta_1}+\boldsymbol{X_2\beta_2}+\boldsymbol{\varepsilon_Y} \textrm{ with } \boldsymbol{\varepsilon_Y} \sim \mathcal{N}(\boldsymbol{0},\sigma^2_Y\boldsymbol{I_n});	\label{MainR}
		\end{equation}
		where $\boldsymbol{\beta}=(\boldsymbol{\beta_1},\boldsymbol{\beta_2}) \in  \mathcal{R}^p$ is the vector of the regression coefficients and $\boldsymbol{I_n}$ the identity matrix. 
We note that (\ref{MainR}) and (\ref{SR}) also give by simple integration on $\boldsymbol{X_2}$ a marginal regression model on $\boldsymbol{Y}$ {\it depending only on uncorrelated covariates $\boldsymbol{X_1}$}:
\begin{eqnarray}
	\boldsymbol{Y}_{|\boldsymbol{X_1},S}&=&\boldsymbol{X_1} (\boldsymbol{\beta_{1}}+ \sum_{j \in I_2}\beta_{j}\boldsymbol{\alpha_j})+  \sum_{j \in I_2}\beta_{j}\boldsymbol{\varepsilon_{j}}+\boldsymbol{\varepsilon_Y} \label{Trueexpl} \\
	&=&\boldsymbol{X_1}\boldsymbol{\beta_1^*}+\boldsymbol{\varepsilon_Y^*}=\boldsymbol{X}\boldsymbol{\beta^*}+\boldsymbol{\varepsilon_Y^*} \textrm{ where }\boldsymbol{\beta^*}=(\boldsymbol{\beta_1^*},\boldsymbol{\beta_2^*}) \textrm{ and } \boldsymbol{\beta_2^*}=\boldsymbol{0}
\end{eqnarray}
We note that it simply is a linear regression on some of the original covariates so we only made a pretreatment on the dataset by setting some coefficients to $0$ because of correlations. These $0$ won't be interpreted as independence with the response variable but as redundant information due to correlations between the covariates. It is a variable pre-selection independent of the response $\boldsymbol{Y}$.

\subsection{Strategy of use: pretreatment before classical selection methods}\label{interpretation}
As a pretreatment, it allows usage of any method in a second time to estimate $\alpha$like LASSO or even stepwise \cite{seber2012linear}.

The explicit structure is parsimonious and simply consists in linear regressions and thus is easily understood by non statistician, allowing them to have a better knowledge of the phenomenon inside the dataset. Expert knowledge can even be added to the structure.

@@

\section{Acknowledgements}
	We want to thanks ArcelorMittal Atlantique \& Lorraine that has granted this work, given the chance to use \textsc{CorReg} on real dataset and authorized the package to be open-sourced licensed (\textsc{CeCILL}), especially Dunkerque's site where most of the work has been done.
\bibliography{biblio}{}
\bibliographystyle{plain}
\section{Appendices}
	\subsection{Identifiability of the structure}
	The model presented above relies on a discrete structure $S$ between the covariates. But to find it we need identifiability property to insure the MCMC will asymptotically find the true model. Identifiability of the discrete structure is asked in following terms: Is it possible to find another structure $\tilde{S}$ of linear regression between the covariates leading to the same joint distribution and marginal distributions? The answer is no. Thus $S$ is identifiable.
